### 2022-04-24 background.tex
Update metrics SISNR
Update SDR metric
Update background formula

Assume there are $N$ speakers talking simultaneously, they are called $s_1, s_2, \dots s_N$. The speech utterance for each speaker is $U_i$ while $i\in\left[ 1, N \right]$. Assume the noise is $e$.
So the mixed utterance $U$ is as equation~\ref{eq:mixed}.
\begin{equation}
    U = \sum\limits_{i=1}^N U_i + e\label{eq:mixed}
\end{equation}
For the mission of Target Speaker Separation (TSS) Task. Assume we only need to extract the voice of speaker $s_n$ and we have the reference utterance from $s_n$, denoted as $R_n$.
The task is given $U = \sum\limits_{i=1}^N U_i + e$ and $R_n$, we need to get $U_n$.

>>>>

Assume there are $N$ speakers talking simultaneously, they are called $s_1, s_2, \dots s_N$. The waveform of speech utterance for each speaker is $U_i\left( t \right)$ while $i\in\left[ 1, N \right]$. Assume the noise is $e\left( t \right)$.
So the mixed utterance $X\left( t \right)$ is as equation~\ref{eq:mixed}.
\begin{equation}
    X\left( t \right) = \sum\limits_{i=1}^N U_i\left( t \right) + e\left( t \right)
    \label{eq:mixed}
\end{equation}
For the mission of Target Speaker Separation (TSS) Task. Assume we only need to extract the voice of speaker $s_n$ from $X\left( t \right)$ and we have the reference utterance from $s_n$, denoted as $R_n$.
The task is given $X\left( t \right) = \sum\limits_{i=1}^N U_i\left( t \right) + e\left( t \right)$ and $R_n$, we need to get $U_n\left( t \right)$.

\subsection{Metrics}\label{subsec:metrics}

Using meaningful metrics to define the performance of the separation system is important.

\begin{itemize}
    \item source-to-distortion ratio (SDR)

    SDR is defined in~\cite{performance_measurement}, and is as equation~\ref{eq:sdr}.
    \begin{equation}
        \text{SDR} \coloneqq 10\log_{10}\frac{\| s_{\text{target}} \|^2}{\| e_{\text{interf}} + e_{\text{noise}} + e_{\text{artif}} \|^2}
        \label{eq:sdr}
    \end{equation}

    \item scale-invariant source-to-noise ratio (SI-SNR)

    SI-SNR is proposed in~\cite{tasnet}, and is as equation~\ref{eq:si-snr}.
    \begin{equation}
        \begin{aligned}
            s_{\text{target}} &= \frac{\left< \hat{s}, s \right>s}{\| s \|^2} \\
            e_{\text{noise}} &= \hat{s} - s_{\text{target}} \\
            \text{SI-SNR} &\coloneqq 10\log_{10}\frac{\| s_{\text{target}} \|^2}{\| e_{\text{noise}} \|^2}
        \end{aligned}\label{eq:si-snr}
    \end{equation}
\end{itemize}

\subsection{Methodology}\label{subsec:methodology}
